### 2013-01-21 edupar-13/410.tex
Cite a different Plan 9 paper.

The kernel that students implement consists of twenty-five
system calls, which are summarized in Figure~\ref{fig:syscalls}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Warning: vanish() is *not* "the Pebbles name for exit()"--
%% exit() used to mean one thing, and now means some other
%% thing which is muddy.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The process lifecycle is loosely based on the
%% Unix model: \x{fork()}, \x{exec()}, \x{wait()},
%% and \x{vanish()} (the Pebbles name for \x{exit()}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The process lifecycle is loosely based on the
Unix \x{fork()}/\x{exec()}/\x{wait()} model.
We adopt the Mach~\cite{DBLP:conf/usenix/AccettaBBGRTY86}
distinction between ``tasks,''
which are resource containers,
and threads,
each of which executes within a single task.
This partitioning is a different approach from that of
Plan~9's \x{rfork()}~\cite{plan9} or Linux's \x{clone()},
both of which allow a continuum of sharing between
identical threads and independent processes,
at the cost of implementation complexity which we wish to avoid.
A task's address space can be edited through two system
calls that add and delete contiguous regions of memory.
Students are expected to implement zero-fill-on-demand,
but copy-on-write and demand-loading of executables are
optional.
Threads can print text to and read lines of text from
the simple console that students implemented at
the start of the semester.

>>>>

The kernel that students implement consists of twenty-five
system calls, which are summarized in Figure~\ref{fig:syscalls}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Warning: vanish() is *not* "the Pebbles name for exit()"--
%% exit() used to mean one thing, and now means some other
%% thing which is muddy.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The process lifecycle is loosely based on the
%% Unix model: \x{fork()}, \x{exec()}, \x{wait()},
%% and \x{vanish()} (the Pebbles name for \x{exit()}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The process lifecycle is loosely based on the
Unix \x{fork()}/\x{exec()}/\x{wait()} model.
We adopt the Mach~\cite{DBLP:conf/usenix/AccettaBBGRTY86}
distinction between ``tasks,''
which are resource containers,
and threads,
each of which executes within a single task.
This partitioning is a different approach from that of
Plan~9's \x{rfork()}~\cite{Pike90plan9} or Linux's \x{clone()},
both of which allow a continuum of sharing between
identical threads and independent processes,
at the cost of implementation complexity which we wish to avoid.
A task's address space can be edited through two system
calls that add and delete contiguous regions of memory.
Students are expected to implement zero-fill-on-demand,
but copy-on-write and demand-loading of executables are
optional.
Threads can print text to and read lines of text from
the simple console that students implemented at
the start of the semester.
